---
title: "Lecture01: Import Data to R"
author: "Jihong Zhang"
date: "November 13, 2017"
output: 
  ioslides_presentation:
    incremental: true
    smaller: true 
    transition: faster
    css: styles.css
    mathjax: "http://example.com/mathjax/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
    widescreen: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Checking Your Data {#nextsteps .smaller .build}

<div class="red3">
The first thing is check your data
</div>

- Your data file type
- Your data save path

You can also highlight R codes:
```{r}
### <b>
x <- 10
y <- x * 2
### </b>
```

## Preparing Your R Workspace {#nextsteps .emphasized}

<div class="red3">
You should always set up your workspace to your working directory first.
</div>

For example, I want to set up my R workspace to dropbox
```{r ,echo=TRUE}
setwd("G:/Dropbox/") # absolute path
getwd() # get your Workspace now
```

You can use the function below to check whether you set up workspace correctly.
```{r ,echo=TRUE}
list.files()
```

You shall see your data files in the output above.


## Read CSV Files into R  | This is a subtitle

In this class, you usually are dealling with **CSV** file.

```{r , eval=FALSE}
library(magrittr)
col1 <- paste(1:5, collapse = ",")
col2 <- paste(1:5, collapse = ",")%>% as.data.frame()
col3 <- paste(1:5, collapse = ",")%>% as.data.frame()
Reduce(list(col1, col2, col3), rbind)
```

- Bullet 1
- Bullet 2
- Bullet 3


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```


## Slide with Plot

```{r pressure}
plot(pressure)
```

